H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-13 slides-agu/presentation.tex
potentially a final version of slides?

% Add footer for AGU
\setbeamertemplate{footline}[text line]{%
  \parbox{0.8\linewidth}{
    \vspace*{-8pt}James Doss-Gollin (\url{james.doss-gollin@columbia.edu})
  }
  \hfill%
  \parbox{0.15\linewidth}{
    \vspace*{-8pt}\raggedleft\insertpagenumber
  }
}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How well can one identify and predict risk}
     associated with cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
  \end{alertblock}
  \pause
  \begin{columns}
    \begin{column}{0.5\textwidth}
      In particular, we consider:
      \begin{itemize}
        \item the specific roles of $M$ and $N$;
        \pause
        \item estimation strategy (few processes/parameters $\Rightarrow$ many processes/parameters)
        \pause
        \item the form of the underlying climate signal.
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{Example-NINO3-M100-N50-Stationary-Trend.pdf}
        \caption{
          What is the bias and spread of $p(X > X^*)$?
          Here, $M=100$ and $N=50$.
          Subsequent results are tested systematically over $J=1000$ sequences.
        }
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Stationary Scenario (LFV Only)}
  Estimating a trend when none exists may lead to substantial over-estimation of risk, particularly for short $N$ or long $M$.
  Explicitly modeling \gls{lfv} improves estimates, particularly for long $N$.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

\begin{frame}{Nonstationary Scenario I (Secular Change Only)}
  For long $M$, it's important to estimate the trend -- but only works well if $N$ also long.
  For short $M$ and short $N$, the uncertainty added by estimating a trend is not worth the bias reduction.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{secular-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

@@

\begin{frame}{Summary}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      Assertions:
      \begin{itemize}
        \item Investment evaluation depends on climate condition over finite planning period
        \item Physical hydroclimate systems vary on many scales
        \item Physical drivers of risk depend on planning period
      \end{itemize}    
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      Implications:
      \begin{itemize}
        \pause
        \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
        \pause
        \item \emph{Importance} of identifying and predicting different climate signals depends on degree of extrapolation desired (\ie, $M$)
        \pause
        \item In general, low risk tolerance and/or short $N$ favor short-$M$ investments relative to long-$M$ ones.
      \end{itemize}    
    \end{column}
  \end{columns}
\end{frame}

@@

\section{Relating our Analysis to Observations}

>>>>

% Add footer for AGU
\setbeamertemplate{footline}[text line]{%
  \parbox{0.8\linewidth}{
    \vspace*{-8pt}James Doss-Gollin (\url{james.doss-gollin@columbia.edu})
  }
  \hfill%
  \parbox{0.15\linewidth}{
    \vspace*{-8pt}\raggedleft\insertframenumber
  }
}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How to identify \& predict}
    cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
 \end{alertblock}
 \pause
  \begin{columns}
    \begin{column}{0.5\textwidth}
      In particular, we consider:
      \begin{itemize}
        \item the specific roles of $M$ and $N$;
        \item estimation strategy
        \item structure of climate signal
      \end{itemize}
      \pause
      To analyze predictions, we assess the \emph{bias} and \emph{variance} of predicted flood occurrence.
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{Bias-Variance-Sketch.pdf}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{Stationary Scenario (LFV Only)}
  With limited data, the uncertainties caused by extrapolating from complex models lead to poor performance.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

\begin{frame}{Nonstationary Scenario I (Secular Change Only)}
  For long $M$, it's important to estimate the trend -- but this works well only if $N$ also long.
  For short $M$ and short $N$, the uncertainty added by estimating a trend is not worth the bias reduction.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{secular-only-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

@@

\begin{frame}{Summary}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      Assertions:
      \begin{itemize}
        \item Investment evaluation depends on climate condition over finite planning period
        \item Physical hydroclimate systems vary on many scales
        \item Physical drivers of risk depend on planning period
      \end{itemize}    
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      Implications:
      \begin{itemize}
        \pause
        \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
        \pause
        \item \emph{Importance} of predicting different climate signals depends on extrapolation desired (\ie, planning period)
        \pause
        \item In general, low risk tolerance and/or limited information favor investments with short planning periods.
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\section{Supplemental Discussion}
